
  \documentclass[twoside]{article}
  \usepackage[affil-it]{authblk}
  \usepackage{lipsum} % Package to generate dummy text throughout this template
  \usepackage{eurosym}
  \usepackage[sc]{mathpazo} % Use the Palatino font
  \usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
  \usepackage[utf8]{inputenc}
  \linespread{1.05} % Line spacing-Palatino needs more space between lines
  \usepackage{microtype} % Slightly tweak font spacing for aesthetics\[IndentingNewLine]
  \usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
  \usepackage{multicol} % Used for the two-column layout of the document
  \usepackage[hang,small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under//above floats in tables or figures
  \usepackage{booktabs} % Horizontal rules in tables
  \usepackage{float} % Required for tables and figures in the multi-column environment-they need to be placed in specific locations with the[H] (e.g. \begin{table}[H])
  \usepackage{hyperref} % For hyperlinks in the PDF
  \usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
  \usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
  \usepackage{abstract} % Allows abstract customization
  \renewcommand{\abstractnamefont}{\normalfont\bfseries} 
  %\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text\[IndentingNewLine]
  \usepackage{titlesec} % Allows customization of titles
  \renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
  \renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
  \titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
  \titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles
  \usepackage{fancyhdr} % Headers and footers
  \pagestyle{fancy} % All pages have headers and footers
  \fancyhead{} % Blank out the default header
  \fancyfoot{} % Blank out the default footer
  \fancyhead[C]{X-meeting $\bullet$ November 2017 $\bullet$ S\~ao Pedro} % Custom header text
  \fancyfoot[RO,LE]{} % Custom footer text
  %----------------------------------------------------------------------------------------
  % TITLE SECTION
  %---------------------------------------------------------------------------------------- 
 
 \title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{ Oncogenic Fusion Gene CD74-NRG1 Confers Cancer Stem Cell-like Properties in Lung Cancer through a IGF2 Autocrine/Paracrine Circuit. }} % Article title
  
  
  \author{ Takahiko Murayama$^{1}$, Tatsunori Nishimura$^{2}$, Kana Tominaga$^{1}$, Asuka Nakata$^{2}$, Noriko Gotoh$^{2}$, }
  
  \affil{ 1 The University of Tokyo

2 Kanazawa University

 }
  \vspace{-5mm}
  \date{}
  
  %---------------------------------------------------------------------------------------- 
  
  \begin{document}
  
  
  \maketitle % Insert title
  
  
  \thispagestyle{fancy} % All pages have headers and footers
  %----------------------------------------------------------------------------------------  
  % ABSTRACT
  
  %----------------------------------------------------------------------------------------  
  
  \begin{abstract}
  The CD74-Neuregulin1 (NRG1) fusion gene was recently identified in invasive mucinous adenocarcinoma of the lung, a malignant type of the lung adenocarcinomas, and is considered to be a new driver gene aberration. However, pathogenic functions of the CD74-NRG1 fusion gene have not yet been understood, and it is unknown whether the driver gene contributes to cancer stem cells (CSCs). Here, we show that expression of the CD74-NRG1 fusion gene induces CSC properties. Expression of CD74-NRG1 facilitated sphere formation of not only cancer cells but also non-cancerous lung epithelial cells. By using a limiting dilution assay in xenograft model, we showed that expression of CD74-NRG1 fusion gene enhances tumor initiating ability. We found that expression of CD74-NRG1 stimulates phosphorylation of ErbB2/3 and activates phosphatidyl inositol 3-kinase (PI3K)/Akt/NF-?B signaling pathway. Furthermore, we found that secreted insulin-like growth factor 2 (IGF2) levels were increased and phosphorylation levels of IGF1 receptor (IGF1R), the receptor for IGF2, were enhanced in a NF-?B activity dependent manner in cells expressing CD74-NRG1. These findings suggest that the CD74-NRG1-stimulated NF-?B activity induces IGF2 autocrine/paracrine loop. In addition, CD74-NRG1 fusion gene-induced tumor sphere formation was suppressed by treatment with inhibitors of ErbB2, PI3K or NF-?B or anti-IGF2 antibody. We thus provide evidence that the CD74-NRG1 fusion protein may not only act as a driver for tumor development but also initiate and maintain CSCs. Inhibition of ErbB/PI3K/Akt/NF-?B signaling pathway or secreted IGF2 are promising therapeutic strategies for CD74-NRG1 fusion positive cancers.
  
  Funding: no \\ 
  \end{abstract}
  \end{document} 